Analysis

### 2023-03-28 Analysis.rmd
Added plots with model ranks

p_performance <- scores |>
  filter(model %in% models_non_human) |>
  mutate(model = factor(model, labels = levels(models_non_human))) |>
  plot_performance()

@@

p_scores_and_pred <- plot_scores_and_pred(
  filter(forecasts, model %in% models_non_human) |>
    mutate(model = factor(model, labels = levels(models_non_human))),
  filter(scores, model %in% models_non_human) |>
    mutate(model = factor(model, labels = levels(models_non_human)))
)

@@

>>>>

p_performance <- scores |>
  filter(model %in% models_non_human) |>
  mutate(model = factor(model, levels = levels(models_non_human))) |>
  plot_performance()

@@

p_scores_and_pred <- plot_scores_and_pred(
  filter(forecasts, model %in% models_non_human) |>
    mutate(model = factor(model, levels = levels(models_non_human))),
  filter(scores, model %in% models_non_human) |>
    mutate(model = factor(model, levels = levels(models_non_human)))
)

@@

# Ranks

plot_ranks <- function(scores, hor = 2) {
  scores |>
    filter(model %in% models_non_human) |>
    mutate(model = factor(model, levels = rev(levels(models_non_human)))) |>
    summarise_scores() |>
    select(model, target_type, horizon, forecast_date, interval_score, scale, type_and_scale) |>
    group_by(target_type, scale, horizon, forecast_date) |>
    mutate(rank = rank(interval_score)) |>
    filter(horizon == hor) |>
    ggplot(aes(y = model, group = rank, fill = rank)) +
    geom_bar(position = position_stack(), colour = "white", size = 0.03) + 
    facet_wrap(~ type_and_scale) + 
    scale_fill_continuous(trans='reverse') + 
    theme_scoringutils() + 
    labs(y = "", x = "Frequency", fill = "Rank") + 
    theme(legend.position = "right")
}

p_ranks <- plot_ranks(scores)
ggsave("output/figures/performance-ranks.png", 
       plot = p_ranks, 
       width = 7, height = 3.4)

p_ranks_4 <- plot_ranks(scores, hor = 4)
ggsave("output/figures/performance-ranks-4.png", 
       plot = p_ranks_4, 
       width = 7, height = 3.4)
